Election Predictions:A Data-Driven Approach to US Election Forecasting

### 2024-11-04 paper/paper.qmd

# References

>>>>

# References
R Core Team. 2023. R: A Language and Environment for Statistical Computing. Vienna,
Austria: R Foundation for Statistical Computing. https://www.R-project.org/.

Rohan Alexander. 2023. Telling Stories with Data. Chapman; Hall/CRC. https://tellingstorieswithdata.com/.

Wickham, Hadley. 2016. Ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New
York. https://ggplot2.tidyverse.org.

Wickham, Hadley, Jim Hester, and Jennifer Bryan. 2024. Readr: Read Rectangular Text Data.
27. https://readr.tidyverse.org.

Emerson. 2024. ECP_Swing_States_10.10.24. https://docs.google.com/spreadsheets/d/1KdGpVQ0P7AVCDB5vsfoukqF6tS2ghVAo/edit?gid=1979448346#gid=1979448346.

Emerson. 2024. October 2024 State Polls: Mixed Movement Across Swing States Shows Dead Heat. https://emersoncollegepolling.com/october-2024-state-polls-mixed-movement-across-swing-states-shows-dead-heat/.
